\Large Taking uncertainty seriously \newline \normalsize A Bayesian approach to word embedding bias estimation

### 2022-03-11 presentations/presentationBoston/presentationBoston.Rmd
Adds lists of human and neutral words

>>>>

### Our lists of neutral and human words

- neutral words = [liquor, pow, ballpark, glitchy, billy, dallas, rip, called, outlooks, viet, floater, rattlesnake, exports,
peruvian, recursion, shortfall, corrected, amicable, solutions, diagnostic, patently, flops, approx, percents, lox, catapults,
hamburger, engulfed, households, north, snubbed, playtest] \newline

- human words = [switch, studio, stick, soup, sometimes, signal, prior, plant, photo, path, park, near, menu, latter, grass, clock, 
wear, walk, visitor, toy, tissue, throw, talk, speak, sleep, eye, enjoy, blogger, character, candidate, breakfast, supper, dinner,
eat, drink, carry, run, cast, ask, awake, ear, nose, lunch]

### 2022-03-11 presentations/presentationBoston/presentationBoston.tex
Adds new table
Adds lists of human and neutral words

\begin{frame}{Some methodological problems}
\protect\hypertarget{some-methodological-problems-2}{}
\begin{block}{Outliers and surprisingly dissimilar words}
\protect\hypertarget{outliers-and-surprisingly-dissimilar-words}{}
We study those by visualizations and uncertainty estimates.
\end{block}
\end{frame}

\begin{frame}{Some methodological problems}
\protect\hypertarget{some-methodological-problems-3}{}
\begin{block}{Distances for ``muslim''}
\protect\hypertarget{distances-for-muslim}{}
\begin{center}\includegraphics[width=0.8\linewidth]{presentationBoston_files/figure-beamer/unnamed-chunk-4-1} \end{center}
\end{block}
\end{frame}

\begin{frame}{Some methodological problems}
\protect\hypertarget{some-methodological-problems-4}{}
\begin{block}{Distances for ``priest''}
\protect\hypertarget{distances-for-priest}{}
\begin{center}\includegraphics[width=0.8\linewidth]{presentationBoston_files/figure-beamer/unnamed-chunk-5-1} \end{center}
\end{block}
\end{frame}

\begin{frame}{Some methodological problems}
\protect\hypertarget{some-methodological-problems-5}{}
\begin{block}{No principled interpretation}
\protect\hypertarget{no-principled-interpretation}{}
\begin{longtable}[]{@{}ll@{}}
\toprule
Religion Debiasing & MAC (distance) \\
\midrule
\endhead
Biased & 0.859 \\
Hard Debiased & 0.934 \\
Soft Debiased (\(\lambda\) = 0.2) & 0.894 \\
\bottomrule
\end{longtable}

@@

\begin{itemize}
\tightlist
\item
  Raw sd in data is 0.045
\item
  The sd of means is 0.023
\item
  The WEAT score is 1.825\\
\item
  The largest effect size reported by
  \protect\hyperlink{ref-Caliskan2017semanticsBiases}{Caliskan, Bryson,
  \& Narayanan}
  (\protect\hyperlink{ref-Caliskan2017semanticsBiases}{2017}) is 1.81!
\end{itemize}
\end{block}
\end{frame}

>>>>

\begin{frame}{Some methodological problems}
\protect\hypertarget{some-methodological-problems-2}{}
\begin{block}{Our lists of neutral and human words}
\protect\hypertarget{our-lists-of-neutral-and-human-words}{}
\begin{itemize}
\item
  neutral words = {[}liquor, pow, ballpark, glitchy, billy, dallas, rip,
  called, outlooks, viet, floater, rattlesnake, exports, peruvian,
  recursion, shortfall, corrected, amicable, solutions, diagnostic,
  patently, flops, approx, percents, lox, catapults, hamburger,
  engulfed, households, north, snubbed, playtest{]} \newline
\item
  human words = {[}switch, studio, stick, soup, sometimes, signal,
  prior, plant, photo, path, park, near, menu, latter, grass, clock,
  wear, walk, visitor, toy, tissue, throw, talk, speak, sleep, eye,
  enjoy, blogger, character, candidate, breakfast, supper, dinner, eat,
  drink, carry, run, cast, ask, awake, ear, nose, lunch{]}
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{Some methodological problems}
\protect\hypertarget{some-methodological-problems-3}{}
\begin{block}{Outliers and surprisingly dissimilar words}
\protect\hypertarget{outliers-and-surprisingly-dissimilar-words}{}
We study those by visualizations and uncertainty estimates.
\end{block}
\end{frame}

\begin{frame}{Some methodological problems}
\protect\hypertarget{some-methodological-problems-4}{}
\begin{block}{Distances for ``muslim''}
\protect\hypertarget{distances-for-muslim}{}
\begin{center}\includegraphics[width=0.8\linewidth]{presentationBoston_files/figure-beamer/unnamed-chunk-4-1} \end{center}
\end{block}
\end{frame}

\begin{frame}{Some methodological problems}
\protect\hypertarget{some-methodological-problems-5}{}
\begin{block}{Distances for ``priest''}
\protect\hypertarget{distances-for-priest}{}
\begin{center}\includegraphics[width=0.8\linewidth]{presentationBoston_files/figure-beamer/unnamed-chunk-5-1} \end{center}
\end{block}
\end{frame}

\begin{frame}{Some methodological problems}
\protect\hypertarget{some-methodological-problems-6}{}
\begin{block}{No principled interpretation}
\protect\hypertarget{no-principled-interpretation}{}
\begin{longtable}[]{@{}lllll@{}}
\toprule
Category & Biased & Hard Debiased & Soft Debiased & Diff \\
\midrule
\endhead
Religion & 0.859 & 0.934 & 0.894 & 0.075 \\
Race & 0.892 & 0.925 & 0.985 & 0.033 \\
Gender & 0.623 & 0.700 & 0.747 & 0.077 \\
\bottomrule
\end{longtable}

@@

\begin{itemize}
\tightlist
\item
  Raw sd in data is 0.072
\item
  The sd of means is 0.037
\item
  The WEAT score is 1.825\\
\item
  The largest effect size reported by
  \protect\hyperlink{ref-Caliskan2017semanticsBiases}{Caliskan, Bryson,
  \& Narayanan}
  (\protect\hyperlink{ref-Caliskan2017semanticsBiases}{2017}) is 1.81!
\end{itemize}
\end{block}
\end{frame}
